### 2025-02-14 paper/sections/other/constraints.qmd
uf

    # Gradient field:
    targets = Flux.onehotbatch(fill(2,size(x,2)), [1,2])
    samples = ce_data.X[:,ce_data.output_encoder.labels.==2][:,rand(1:end,size(x,2))]
    u = []
    v = []
    η = 0.1
    for (i,ce) in enumerate(eachcol(x))
        grads = Flux.gradient((m,x,s,t) -> implausibility(m,x,s,t)[1], model, ce, samples[:,i], targets[:,i])
        g = grads[1].layers[1].weight
        push!(u, η * g[1])
        push!(v, η * g[2])
    end
    Plots.quiver!(x1, x2, quiver=(u, v))

@@

# Data:
specs = [
    ("(a)", VanillaObjective(needs_ce=true), ["both", "both"]),
    ("(b)", EnergyDifferentialObjective(lambda=[1.0,1.0,0.0]), ["both", "both"]),
    ("(c)", EnergyDifferentialObjective(lambda=[1.0,1.0,0.0]), ["both", "none"]),
]
```

@@

    model, logs = counterfactual_training(
        obj,
        model,
        generator,
        train_set,
        opt_state;
        val_set = val_set,
        nepochs = 5,
        mutability = Symbol.(constraint),
        callback = plot_db,
        nce=50,
        convergence=conv, 
    )

>>>>

    # Gradient field:
    targets = Flux.onehotbatch(fill(2,size(x,2)), [1,2])
    samples = ce_data.X[:,ce_data.output_encoder.labels.==2][:,rand(1:end,size(x,2))]
    CounterfactualTraining.protect_immutable!(eachcol(samples), eachcol(x), ce_data.mutability)
    u = []
    v = []
    η = 0.5
    for (i,ce) in enumerate(eachcol(x))
        grads = Flux.gradient((m,x,s,t) -> implausibility(m,x,s,t)[1], model, ce, samples[:,i], targets[:,i])
        g = CTExperiments.get_log_reg_params(grads[1].layers[1])
        push!(u, η * g[2])
        push!(v, η * g[3])
    end
    Plots.quiver!(x[1,:], x[2,:], quiver=(u, v))

@@

# Data:
specs = [
    # ("(a)", VanillaObjective(needs_ce=true), ["both", "both"]),
    # ("(b)", EnergyDifferentialObjective(lambda=[1.0,1.0,0.0]), ["both", "both"]),
    ("(c)", EnergyDifferentialObjective(lambda=[1.0,1.0,0.0]), ["both", "none"]),
]
```

@@

    model, logs = counterfactual_training(
        obj,
        model,
        generator,
        train_set,
        opt_state;
        val_set = val_set,
        nepochs = 25,
        mutability = Symbol.(constraint),
        callback = plot_db,
        nce=50,
        convergence=conv, 
    )
